Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:05	17:58:18	(Wed 5.Aug)

@@

Variables of interest:
\begin{itemize}
\item Window function. Mostly symmetrical, in particular in shadow and for the most part in speckle. In highlight regions more varying.
\item Mainlobe width. Wide in shadows, narrow in detailed regions. Adding windows in between these extremal values.
\item Steering. No steering in shadows, slight steering in speckle and no steering in highlight. Steering more than the -3dB width of the window function has no effect.
\item Oversampling. From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to 8M.
\end{itemize}

\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry             & Moderate  & High   & High \\
Mainlobe width       & Narrow    & Wide   & Moderate \\
Sidelobe suppression & Low       & High   & Moderate \\
Steering             & Low       & Up to -3dB width & Moderate \\
Oversampling         & 2x-8x     & 2x-8x  & 2x-8x
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%

@@

\begin{itemize}
\item \emph{Window function}. A Kaiser window was chosen due to its resemblance to typical MVDR responses for shadow, speckle and highlight regions in an image, as shown in \Fig{mvdr_selected_windows}.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ tunes the compromise between resolution and sidelobe suppression. At $\beta=0$ ) and a gaussian curve (
\end{itemize}

@@

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.5\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{windows_steering}
\end{figure*}

@@

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.5\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

>>>>

\begin{figure}[tbhp]%\centering%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{windows_steering}
\end{figure}

@@

@@

\begin{itemize}
\item \emph{Window function}. A Kaiser window was chosen due to its resemblance to typical MVDR responses for shadow, speckle and highlight regions in an image, as shown in \Fig{mvdr_selected_windows}.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression, and $\phi$ controls the amount of steering.. $\beta=0$ ) and a gaussian curve (
\end{itemize}

@@

\subsection{Window parameters}

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.2\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

@@

Variables of interest:

\begin{itemize}
\item Window function. Mostly symmetrical, in particular in shadow and for the most part in speckle. In highlight regions more varying.
\item Mainlobe width. Wide in shadows, narrow in detailed regions. Adding windows in between these extremal values.
\item Steering. No steering in shadows, slight steering in speckle and no steering in highlight. Steering more than the -3dB width of the window function has no effect.
\item Oversampling. From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to 8M.
\end{itemize}
\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry             & Moderate  & High   & High \\
Mainlobe width       & Narrow    & Wide   & Moderate \\
Sidelobe suppression & Low       & High   & Moderate \\
Steering             & Low       & Up to -3dB width & Moderate \\
Oversampling         & 2x-8x     & 2x-8x  & 2x-8x
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%
